Article Title

### 2013-11-19 cosyne/Yatsenko-Cosyne-2014.tex
final version of the CoSyNe abstract

We then estimated the correlation matrices of population calcium signals of large groups of cells (91--314 neurons, averarge 206 in 31 sites from 24 animals) in small volumes of visual cortex during visual stimulation \cite{Cotton:2013}. We found that the sparse+latent estimator consistently outperformed all other estimators (data to be presented).

In addition to minimizing the estimation error, the sparse+latent estimator revealed sparse networks of linear interactions such as shown in \autoref{fig:reconstruction} and several shared latent units (not shown).
Individual imaged sites varied greatly in the number of significant latent units and the sparsity of direct interations (data to be presented).
We analyzed how the distribution of these interactions compared to the distribution of the usual sample correlations as a function of the difference in preferred orientation, vertical distance, and lateral distance in the cortex \autoref{fig:summary}. The patterns of inferred interactions differed substantially from patterns of most significant correlations (data to be presented).
\begin{multicols}{2}
\begin{Figure}
  \includegraphics{./Reconstruction.pdf}
  \captionof{figure}{An example of 3D arrangement of recorded cells with color-coded orientation preference and edges indicating the network of positive (green) and negative interactions (magenta) as revealed by the sparse+latent estimator. The latent units are not shown.}
  \label{fig:reconstruction}
\end{Figure}

@@

\subsubsection*{Significance}
In this empirical study, we identified the most efficient of several estimators of correlation matrices of activity fluctuations in cortical microcircuits. The resulting estimates effectively decomposed the correlation structure into direct interactions between pairs of neurons and common diffuse fluctuations. The physiological interpretation of these components remains in question and must be addressed by additional experiements where synaptic connectivity, cell types, and local field potentials may be used to corroborate such interpretations.

>>>>

We then estimated the correlation matrices of population calcium signals of large groups of cells (91--314 neurons, average 206 in 31 sites from 24 animals) in small volumes of visual cortex during visual stimulation \cite{Cotton:2013}. We found that the sparse+latent estimator consistently outperformed all other estimators (data to be presented).

In addition to minimizing the estimation error, the sparse+latent estimator revealed sparse networks of linear interactions such as shown in \autoref{fig:reconstruction} and several shared latent units (not shown).
Individual imaged sites varied greatly in the number of significant latent units and the sparsity of direct interactions (data to be presented).
We analyzed how the distribution of these interactions compared to the distribution of the usual sample correlations as a function of the difference in preferred orientation, vertical distance, and lateral distance in the cortex \autoref{fig:summary}. The patterns of inferred interactions differed substantially from patterns of most significant correlations (data to be presented).
\begin{multicols}{2}
\begin{Figure}
  \includegraphics{./Reconstruction.pdf}
  \captionof{figure}{An example of 3D arrangement of recorded cells with color-coded orientation preference and edges indicating the network of positive (green) and negative interactions (magenta) as revealed by the sparse+latent estimator. The latent units are not shown.}
  \label{fig:reconstruction}
\end{Figure}

@@

\subsubsection*{Significance}
In this empirical study, we identified the most efficient of several estimators of correlation matrices of activity fluctuations in cortical microcircuits. The resulting estimates effectively decomposed the correlation structure into direct interactions between pairs of neurons and common diffuse fluctuations. The physiological interpretation of these components remains in question and must be addressed by additional experiments where synaptic connectivity, cell types, and local field potentials may be used to corroborate such interpretations.
